Codebook
========

In this codebook, we will take a brief look into the tidy dataset that we generate in this project.

Input data
----------
The program used the following files to generate the final tidy data.
* ../train/X_train.txt
* ../test/X_test.txt
* ../train/y_train.txt
* ../test/y_train.txt
* ../test/subject_test.txt
* ../train/subject_train.txt
* activity_labels.txt
* features.txt

They are available at:
`https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip`.

Data Cleaning
-------------
In the data cleaning process, we did the fellowing 5 steps to get our final tidy dataset.
For more information you can check the R code of this part at 'run_analysis.R'

1. Merges the training and the test sets to create one data set.
2. Extracts only the measurements on the mean and standard deviation for each measurement. 
3. Uses descriptive activity names to name the activities in the data set
4. Appropriately labels the data set with descriptive variable names. 
5. From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.

Dataset structure
-----------------

```{r}
str(tidy_data)
```

Summary of variables
--------------------

```{r}
summary(tidy_data)
```